Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-22 paper/paper.tex
sm changes to introduction, systems engineering, itemize itemsep

We would like to acknowledge
(Adrien's Father), for his prolific networking and promoting of the team;
Gregg (last name) of BP Hobbies for going out of his way to help us;
David Devries and Michael Maia, for their technical guidance;
Professor Chung-chieh Shan, for overseeing Pat's independent study on the IMU design;
Ivan Seskar, for keeping us (and many other undergrads) in the black;
Roger Kondos and Brij Pathak, for contributing to the thermopile attitude sensor.

@@

One of the most difficult design decisions was to quantify ``ample payload.'' The payload size and weight is the major determining factor in the aircraft size.
% -- expand this thought: 
We started off assuming an electronics (computer + batteries) payload of 2.5lbs and a pan-tilt camera of 2.5lbs and 8 inch diameter.

@@

The electronics team was in charge of the autopilot system and the imaging system.

@@

At the time of this writing, we have completed and flown a single flight vehicle, which we have named the \emph{Daedalus}.
We have also nearly completed a very similar backup airframe which serve as a backup in case the \emph{Daedalus} has a disaster. The \emph{Knight Two} will be fitted with

@@

Figure goes here: Photos of Knight Two in construction, sandbag testing

@@

We needed to interface with the following hardware components:
\begin{itemize}
	\item GPS
	\item servos
	\item camera
	\item etc.
\end{itemize}

@@

\begin{figure} [H]
  \centering
  	\includegraphics[width=0.9\textwidth]{../images/ImageStationControls.jpg}
  	\caption[Image Station Control Panel]{The Control Panel for the Image Station.  Above is a live video feed from the plane.  Below are controls to adjust the pan/tilt of the unit, zoom in/out, take a picture, and reset the camera to a neutral position.}
  	\label{imagestationcontrols}
\end{figure}

@@

\begin{figure} [h]
  \centering
  	\includegraphics[width=0.9\textwidth]{../images/ImageStationMain.jpg}
  	\caption[Image Station Interface]{The main interface for the Image Station.  All the images that have been taken are displayed on the top left.  The queue of images to download is on the bottom left.  On the right is the currently displayed image, with target information underneath.}
  	\label{imagestationinterface}
\end{figure}

@@

\subsection{Safety Features}
Our system is designed to gracefully handle any failure while continuing to ensure the safety of those nearby.
\begin{itemize}
\item Channel 5 (?) allows quick switch to safety pilot in case of autopilot malfunction
\item autopilot return home command if connection is lost (I presume it does something like that?)
\item kill switch
\item etc?
\end{itemize}

>>>>

We would like to acknowledge
(Adrien's Father), for his prolific networking and promotion of the team;
Gregg (last name) of BP Hobbies for getting us out of numerous binds;
Dave Devries and Michael Maia, of Invensense, for their technical guidance;
Professor Chung-chieh Shan, for overseeing Pat's independent study on the IMU design;
Ivan Seskar, for keeping us (and many other undergrads) in the black;
Roger Kondos and Brij Pathak, for contributing to the thermopile attitude sensor.

@@

One of the most difficult design decisions was to quantify ``ample payload.'' The payload size and weight is the major determining factor in the aircraft size.
% -- expand this thought pch: 
We started off assuming an electronics (computer + batteries) payload of 2.5lbs and a pan-tilt camera of 2.5lbs and 8 inch diameter.

@@

The electronics team was in charge of the autopilot system and the imaging system. 
% not sure what i want to do to expand here pch

@@

At the time of this writing, we have completed and flown a single flight vehicle, which we have named the \emph{Daedalus}.
We have also nearly completed a very similar backup airframe which serve as a backup in case the \emph{Daedalus} has a disaster. The \emph{Knight Two} will be fitted with nearly identical R/C flight electronics, and accept the same autopilot and imaging system payload as the \emph{Daedalus}

@@

Figure goes here: Photos of Knight Two in construction

@@

We needed to interface with the following hardware components:
\begin{itemize}
	\setlength{\itemsep}{0cm}
	\setlength{\parskip}{0cm}
	\item GPS
	\item servos
	\item camera
	\item etc.
\end{itemize}

@@

\begin{figure} [H]
  \centering
  	\includegraphics[width=0.9\textwidth]{../images/ImageStationControls.jpg}
  	\caption[Image Station Control Panel]{The Control Panel for the Image Station.  Above is a live video feed from the plane.  Below are controls to adjust the pan/tilt of the unit, zoom in/out, take a picture, and reset the camera to a neutral position.}
  	\label{fig:imagestationcontrols}
\end{figure}

@@

\begin{figure} [h]
  \centering
  	\includegraphics[width=0.9\textwidth]{../images/ImageStationMain.jpg}
  	\caption[Image Station Interface]{The main interface for the Image Station.  All the images that have been taken are displayed on the top left.  The queue of images to download is on the bottom left.  On the right is the currently displayed image, with target information underneath.}
  	\label{fig:imagestationinterface}
\end{figure}

@@

\subsection{Safety Features}
Our system is designed to gracefully handle any failure while continuing to ensure the safety of those nearby. 
\begin{itemize}
	\setlength{\itemsep}{0cm}
	\setlength{\parskip}{0cm}
	\item Channel 5 (?) allows quick switch to safety pilot in case of autopilot malfunction
	\item autopilot return home command if connection is lost (I presume it does something like that?)
	\item kill switch
	\item etc?
\end{itemize}
